Setup Honeypot: Team Contagiarium

### 2011-11-01 Setup_honeypot.tex
snort

\subsection{Snort}

Stukje Joost en Bart.

>>>>

\subsection{Snort}
Snort is a network intrusion detection system (NIDS) that uses realtime traffic analysis and packet logging on internet protocol networks.
we use it to detect several attacks including stealth port scans, buffer overflows and more. Snort can be used as a network intrusion prevention system, however we will only be using it to detect attacks.
Snort is rule-based, but we only intend to setup a few general rules that will only alert to suspicious network behaviour and do nothing to prevent it. 
If a rule is triggered, we can look at the logs from the packet logger to analyse the network traffic.
Snort sends alerts and packet logging files to syslog and as stated earlier, the syslog log files are transfered to the remote util machine.
